\subsection{Astrometric and Photometric Calibration}

TODO: rework next paragraph to generalize to photometry, since the same pattern is true for both.

Astrometric calibration is performed in two steps.
First, an astrometric fit is done for single frames, which produces an astrometric solution sufficient for Alert Production and difference imaging.
A final astrometric solution is then fit using the ensemble of images from a given band overlapping with a given tract.
This final astrometric solution is then used for all downstream tasks.
A full description of astrometric calibration in the pipeline is given in \citet{DMTN-266}.

\subsubsection{Single-Frame Astrometric Calibration}

Single frame astrometric fits are performed by \texttt{AstrometryTask} in \texttt{meas\_astrom} and run in \texttt{CalibrateImage} (TODO: crosslink?).
This task matches a catalog of sources detected and measured on an image to a reference catalog and solves for the \textit{World Coordinate System} (WCS) of the image.
Matching and WCS fitting are performed iteratively, to reject astrometric outliers.
The matcher is either the optimistic (\texttt{MatchOptimisticBTask}) or pessimistic (\texttt{MatchPessimisticBTask}) matcher from \citet{2007PASA...24..189T}, with the pessimistic matcher used by default due to better performance on dense fields; see \citep{DMTN-031} for details.
The WCS fitter can be a simple affine model on top of the known camera geometry (TODO: link to afw cameraGeom section!), as in \texttt{FitAffineWcsTask}, or a FITS TAN-SIP WCS \citep{2005ASPC..347..491S}, as in \texttt{FitTanSipWCSTask} or \texttt{FitSipDistortionTask}.
We default to fitting the simple affine model because we have a well fit distortion model from running \texttt{gbdes} in DRP (\S\ref{sec:gbdes}), thus we do not need the extra degrees of freedom provided by a TAN-SIP model.

Because \texttt{AstrometryTask} only requires a single image, it is suitable for use during Alert Production, which does not have access to the entire focal plane.
This single frame astrometric fit is sufficient for initial calibration and difference imaging (assuming the modeled camera geometry is a close match to the true camera distortions), but during DRP we perform a full focal plane fit with \texttt{gbdes}.

\subsubsection{GBDES}
\label{sec:gbdes}

The final astrometric solution is fit by \texttt{GbdesAstrometricFitTask} in \texttt{drp\_tasks}, which runs the \texttt{wcsfit} fitter from the \texttt{gbdes} package \citep{2022ascl.soft10011B,2017PASP..129g4503B} on the ensemble of images in a given band overlapping with a given tract.
This task fits a per-detector polynomial distortion model, a per-exposure polynomial distortion model, and position for all the isolated star sources in the component images.
This is done by first associating all isolated point sources in the input images and matching them with an external reference catalog.
The model is then fit by iterating between fitting the per-detector and per-exposure polynomial models, and recalculating the best-fit solution for the object positions.

The task can be configured to fit either a two-parameter (position on the sky) or five-parameter (position, proper motion, and parallax) solution for the input objects.
Correcting for differential chromatic refraction is another configurable option.

There are also options to run variants of the main \texttt{GbdesAstrometricFitTask}: \texttt{GbdesAstrometricMultibandFitTask} fits images from multiple bands at once, in which case the per-detector distortion model is also per-band; \texttt{GbdesGlobalAstrometricFitTask} removes the restriction to a single tract and fits images regardless of their location on the sky by splitting the images into contiguous groups; \texttt{GbdesGlobalAstrometricMultibandFitTask} combines these two options.

Lastly, the per-detector polynomial model fit by the task is also used to build a camera distortion model, which can be fed back into single-frame modeling or into the \texttt{gbdes} fit for other data.
For use in single-frame modeling, the \texttt{BuildCameraFromAstrometryTask} subtask is used to build an \texttt{afw} Camera object out of the native polynomial model.

\subsubsection{Single-Frame Photometric Calibration}
\label{sec:PhotoCal}

TODO: Eli should look at this?
Single frame photometric calibration is performed by \texttt{PhotoCalTask}, in the \texttt{pipe\_tasks} package.
This task requires that the input catalog come from an image with a good astrometric solution.
The catalog to be calibrated is down-selected to be bright ($S/N>10$), well measured, PSF-like sources which are then matched to a reference catalog.
The matched sources have their instrumental fluxes converted into rough magnitudes, which are are iteratively compared with the reference catalog magnitudes using a sigma-clipping algorithm, to fit a single magnitude zero point to the whole image.

Because \texttt{PhotoCalTask} only requires a single image, it is suitable for use during Alert Production, which does not have access to the entire focal plane.
This single frame photometric fit is sufficient for initial calibration and difference imaging (assuming the flat field calibrations applied during ISR are a close match to the true instrument response), but during DRP we perform a full focal plane fit with \texttt{gbdes}.

\subsubsection{FGCM}
\label{sec:fgcmcal}

Global photometric calibration is computed by use of the Forward Global Calibration Method~\citep[FGCM][]{2018AJ....155...41B}, as adopted for LSST Science Pipelines~\citep{SITCOMTN-086}.
This global calibration algorithm makes use of repeated observations of stars in all $ugrizy$ bands, combining a forward model of the atmospheric parameters with instrumental throughputs measured with auxiliary information.
In this way we simulateously constrain the atmospheric model as well as standardized top-of-atmosphere (TOA) star fluxes over a wide range of star colors, including full chromatic corrections from the instrument and atmosphere.

Running \texttt{fgcmcal} first requires generating a look-up table.
The input to the look-up table includes the effect of a MODTRAN~\citep{10.1117/12.366388} atmospheric model at the elevation of the observatory, as well as the throughput as a function of wavelength and position from the optics, filters, and detector quantum efficiency.
The quality of the output (in terms of repeatability of bright isolated stars across a wide range of colors) depends on the knowledge of the instrumental throughput.

The primary goal of fgcmcal is to provide a uniform relative photometric calibration of the survey.
For ``absolute'' (relative) calibration, a reference catalog can be used as an additional constraint on the fit.
Thus, the overall throughput output by \texttt{fgcmcal} depends on the reference catalog.
This can be checked with (e.g.) specific white dwarfs or CALSPEC~\citep{2007ASPC..364..315B} stars in the survey.
However, the relative spatial and chromatic calibration of the \texttt{fgcmcal} calibration means that the absolute calibration reduces to a set of 6 numbers (one for each band, or one overall throughput and 5 absolute colors).

\subsubsection{jointcal}

\texttt{jointcal} fits both astrometry and photometry across multiple exposures of large mosaic cameras, fitting for both the true star positions/fluxes, and the distortions caused by the telescope and instrument.
\texttt{jointcal} is no longer used used by the LSST camera pipeline, but is available for use by cameras that are not supported by \texttt{gbdes} and/or \texttt{fgcmcal} (for example, DECam).
More details on the \texttt{jointcal} algorithm are available in \citep{DMTN-036}.
