\section{Introduction}
\label{sec:intro}

The NSF-DOE Vera C.\ Rubin Observatory will be performing the 10-year Legacy Survey of Space and Time \citep[LSST;][]{2019ApJ...873..111I} starting in 2026.
Rubin Observatory is located on Cerro Pach\'on in Chile and consists of the 8.4\,m Simonyi Survey Telescope \citep{2022SPIE12182E..0WT} with the 3.2-gigapixel LSSTCam survey camera \citep{10.71929/rubin/2571927,2024SPIE13096E..1SR} performing the main survey and the Rubin Auxiliary Telescope \citep{2020SPIE11452E..0UI} providing supplementary atmospheric calibration data using the LATISS instrument \citep{10.71929/rubin/2571930}.
The Data Management System \citep[DMS;][]{2025ASPC..538...53O} is designed to handle the flow of data from the telescope, approaching 10\,TB per night.
It produces the prompt data products, including alerts, and prepares annual data releases.
A central component of the DMS is the LSST Science Pipelines software, which provides the algorithms and frameworks required to process LSST data  and produce science-ready data products, including coadds, difference images, and catalogs.

The LSST Science Pipelines software consists of the building blocks and infrastructure required to construct high performance pipelines to process the data from the LSST.
It use used both for Data Release Production (DRP) and Alert Production (AP).
It has been under development since at least 2004 \citep{2004AAS...20510811A} and has evolved significantly over the years as the project transitioned from prototyping \citep{2010SPIE.7740E..15A} and entered into formal construction \citep{2017ASPC..512..279J}.
The software is open-source and is designed to be usable by other optical telescopes, a capability that has been demonstrated with the processing of data from Hyper Suprime-Cam (HSC) on the Subaru Telescope in Hawaii \citep{2022PASJ...74..247A} as well as data from additional instruments used for internal testing.
There have also been plugins developed by the community for other instruments.
It was used to make the first public data release from Rubin Observatory, the LSST Data Preview 1 \citep{RTN-095,10.71929/rubin/2570308}, which consisted of data from the LSST Commissioning Camera \citep[LSSTComCam;][]{10.71929/rubin/2561361,2022SPIE12184E..0JS}.

In this paper we provide an overview of the software system, dividing it into four rough tiers:
\begin{itemize}
\item infrastructure consisting of low-level utility code \secrefp{sec:support}, data access, configuration, and execution frameworks \secrefp{sec:middleware}, and the core algorithmic primitives \secrefp{sec:core};
\item reusable mid-level algorithmic components \secrefp{sec:components};
\item high-level tasks and pipelines, along with some details of the algorithms specific to them \secrefp{sec:tasks-and-pipelines};
\item analysis and validation tooling \secrefp{sec:analysis}.
\end{itemize}
There are no sharp boundaries between these tiers; they are better considered to be a loose organizational aid than any kind of formal classification.
We do not include details of the science validation of the individual algorithms, and do not attempt to cover components of the system in uniform detail; instead we focus attention on those that are unique or novel or not well described elsewhere.
The other components of the LSST DMS, such as the workflow system \citep{2025ASPC..538..325G,2024EPJWC.29504026K}, the Qserv database \citep{Wang:2011:QDS:2063348.2063364,2025ASPC..538..114M} and the Rubin Science Platform \citep{LSE-319,2024ASPC..535..227O}, are not covered in this paper.
